Energy and the CES production function

### 2015-08-24 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Minor edits.

    # return this.  ### No need to name and store it.
    melt(
      trimmed_historical_data, 
      measure.vars = measure.vars, 
      value.name = "value",
      variable.name = "variable") %>%
    mutate(
      variable = as.character(variable) # eliminate factors, which cause warnings with bind_rows() below.
      )
  }
  ) %>%

  bind_rows() %>%

@@

historicalPlot(
  histDataForGraph, 
  mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
  # facet_formula = Country ~ flavor, 
  facet_formula = flavor ~ Country, 
  line_types = c(1,2,4,3,2,4,3,2,3,2,3)) + 
xlab("") + 
scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12), limits=c(0.5, 12)) +
ylab("Indexed (1960=1)") +
scale_fill_discrete(breaks=c("y", "k", "l", "e"))

@

>>>>

    # return this.
    melt(
      trimmed_historical_data, 
      measure.vars = measure.vars, 
      value.name = "value",
      variable.name = "variable") %>%
    mutate(
      variable = as.character(variable) # eliminate factors, which cause warnings with bind_rows() below.
      )
  }
  ) %>% bind_rows() %>%

@@

historicalPlot(
  histDataForGraph, 
  mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
  # facet_formula = Country ~ flavor, 
  facet_formula = flavor ~ Country, 
  line_types = c(1,2,4,3,2,4,3,2,3,2,3)) + 
xlab("") + 
scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12), limits=c(0.5, 12)) +
ylab("Indexed (1960=1)") +
scale_fill_discrete(breaks=c("y", "k", "l", "e"))
@
